% resume.tex
%
% (c) 2011 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 20013 Radoslav Stefanov <radoslav@rstefanov.info> http://www.rstefanov.info
%
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\usepackage{hyperref}
\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large Radoslav Stefanov}  & 359 876 305 776\\
Izgrev&
\href{mailto:radoslav@rstefanov.info}{radoslav@rstefanov.info} \\
Sofia, BG&
\href{http://resume.rstefanov.info}{resume.rstefanov.info} \\
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Work Experience}
\begin{itemize}
\item
  \ressubheading{Hostopia Bulgaria / Deluxe Corp}{Sofia, BG}{Linux Systems Administrator and Release Engineering tooling}{February 2014 - Present}
	\begin{itemize}
								\resitem{Provide automation, management, security, performance-tuning and last tier support for approximately 1400 Ubuntu Linux servers.}
                \resitem{Architecture, design, deployment and support for large GitLab EE cluster.}
								\resitem{Backup and disaster recovery tooling and procedures for our whole infrastructure (dev, qa, staging and production).}
								\resitem{Extensive development for our in-house perl based site builder.}
								\resitem{Implemented CI/CD pipliene accross the board.}
								\resitem{Design and implementation of Ansible-based configuration management and provisioning for all new server deployments.}
								\resitem{Docker implementation, automation, upgrade and disaster recovery.}
								\resitem{Platform migration from Leacy Ubuntu 6.06LTS to modern Ubuntu 16.04LTS servers architecture.}
	\end{itemize}
\item
	\ressubheading{Reflective Solutions}{Sofia, BG}{L2 Tech Support Engineer}{February 2013 - February 2014}
	\begin{itemize}
                \resitem{Provide support for medium sized Windows domain infrastructure.}
                \resitem{Help managing Active Directory and Microsoft Exchange clusters.}
                \resitem{Configure and	maintain stress testing, performance management and qa platform for web applications.}
	\end{itemize}

\item
	\ressubheading{DirectHost.BG/HostLine.BG}{Sofia, BG}{Linux Systems Administrator}{May 2011 - December 2012}
	\begin{itemize}
                \resitem{General and On-Call duties in a large (20.5M views/day) and fast-paced Drupal web environment.}
                \resitem{Designed and deployed multi-node Graphite cluster for metric storage and display; began alerting of off metrics.}
                \resitem{Proof of concept for migration from Nagios with NagioSQL configuration to Icinga with Puppet-generated configuration.}
	\end{itemize}

\item
	\ressubheading{BgMreja}{Sofia, BG}{Technical Support}{August 2009 - April 2011}
	\begin{itemize}
                \resitem{Technical support dutties over the phone.}
	\end{itemize}
\end{itemize}

\resheading{Education}
\begin{itemize}
\item
	\ressubheading{Epping Forest College}{London, UK}{ICT, Maths and Further Maths}{January 2006 - October 2008}

\item
  \ressubheading{GPCHE Petar Bogdan}{Montana, BG}{Dual Major, English and German languages}{September 2000 - June 2004}
\end{itemize}

\resheading{Skills}

\begin{description}
\item[Languages:]
Current languages: Bash (six years). Basic or previous knowledge of PHP, Perl.
% using linux since 2002. Admin since 2011.
\item[Operating Systems:]
Six years experience in use and administration of Linux; four years experience architecting and administering production Linux servers and applications.
Primarily CentOS/RedHat/Ubuntu on servers and AWS, Arch Linux and Gentoo Linux personally. Experience with Vyatta Network OS/VyOS, Cisco CatOS and IOS.
\item[Software:]
Many Amazon (AWS) offerings. Vault, Consul, Packer, and related tools. Jenkins. GitLab. Git. Docker. Ansible. Puppet. Graphite, Logstash/Elasticsearch, rsyslog, Nagios/Zabbix/Icinga. MySQL, PostgreSQL. Apache httpd, Nginx.
Former experience with Solr, Postfix, ISC BIND9, ISC dhcpd, FreeRADIUS, Asterisk, OpenLDAP, StrongSwan.

\item[Platforms:]
AWS. Experience with many datacenter technologies: Xen, VMWare, most Enterprise-grade server hardware, F5 Big-IP Load Balancers, network hardware, embedded devices, Meru and BlueSocket wireless hardware. Experience in datacenter operations and physical infrastructure (copper/fiber/power) management.
\end{description}

\resheading{Open Source Projects and Contributions}
\begin{description}
\item{See \href{http://resume.rstefanov.info}{resume.rstefanov.info} for highlights or \href{https://github.com/radoslav-stefanov}{https://github.com/radoslav-stefanov}.}
\end{description}

\end{document}
